{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-18 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

        We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
        It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case, and it relaxes the conditions on the momentum sequence.

        We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
        Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications. 
        We do net yet have a proof for the convergence of the algorithm in general.

@@

    \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Let $0 \le \mu < L$ be the strong convexity and Lipschitz smoothness parameter of $f$. 
        Given iterates $(v_k, x_k)$, or equivalently $(y_k, x_k)$, $(x_k, y_k)$, any $\alpha_k \in (0, 1), \gamma > 0$, the algorithm generates scalar $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ by equalities: 
        \begin{align*}
            \hat \gamma &:= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        We have $x_k, y_k, v_k$ lie on the same line because and they have the following equivalent equalities: 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\hat\gamma/\alpha_k \gamma$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line because (Q1) indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.

@@

        Fix any integer $k \ge0$, assume $v_{k + 1}, x_{k + 1}, y_k, g_k, \hat \gamma$ are produced by Definition \ref{def:stepwise-wapg}. 
        Given any $R_k$.

@@

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$ or equivalently: $(x_1, y_1), (y_1, v_1)$. 
        The algorithm generates a sequence of vector $(x_k, y_k, v_k)$ and auxiliary sequence $\alpha_k, \rho_k$ such that they satisfy for all $k\ge 1$: 
        $$
        \begin{aligned}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
                \\
                \gamma_1 & k = 1. 
            \end{cases}\right\rbrace,
            \\
            \text{find }&\alpha_k \in (0, 1), \rho_k > 0: L\alpha_k^2 = (1 - \alpha_k)\gamma_k + \mu \alpha_k  \;\wedge \; 0 < \rho_k \alpha_k^2 < 1, 
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{aligned}
        $$
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
        The initial condition is generic so it can describe accelerated proximal gradient method in the middle of its executions. 
        \par
        We only need any two of the intertes among $x_1, y_1, v_1$ because we can solve 
        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$ given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$. 
        \par
        % Usually, people initialize the method with one step of gradient descent. 
        % For example, given any $y_0 = x_{0} = v_0\in \RR^n$, we can choose the initial condition $(x_1, v_1)$ to be $v_1 = x_1 = T_L y_{0}$,

    \end{observation}
    \begin{observation}\label{obs:r-wapg-observation-1}
        If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
        \begin{align*}
            \alpha_k &= 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \pm
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right). 
        \end{align*}
        Choosing the positive sign which is the larger one of the roots of the quadratic. 
        We have $\alpha_k > 0$ because: 
        \begin{align*}
            \alpha_k &=
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right)
            \\
            &\ge 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
            \\
            & > 0. 
        \end{align*}
        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
        An upper bound can be identified by using inductive hypothesis and considering: 
        \begin{align*}
            \alpha_k &= 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right)
            \\
            &<
            \frac{1}{2}\left(
                \frac{\mu}{L} + 
                \sup_{x \in (0, 1)}
                \left\lbrace
                    -x + \sqrt{(x - \mu/L)^2 + 4x}
                \right\rbrace
            \right)
            \\
            & \le \frac{1}{2}\left(
                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
            \right) \le 1. 
        \end{align*}
        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
        However, the limit of $\alpha_k$ could be 1. 
    \end{observation}

    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}
        Let vectors $(x_k, y_k, v_k)_{k \ge 1}$ and scalars $\alpha_k$ be generated by R-WAPG (Definition \ref{def:wapg}). 

@@

        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is arbitrary choices for the theorem, we choose $\gamma = \rho_{k - 1} L \alpha_{k - 1}^2 > 0, \hat \gamma = L \alpha_k^2 > 0$ at each step. 
        Because $\alpha_k \in(0, 1)$ by Observation \ref{obs:r-wapg-observation-1}, we can use Proposition \ref{prop:stepwise-lyapunov}: 

@@

        Additionally, the algorithm converges by considering $R_k$: 

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} for the specific initial conditions $\gamma_0 \in(0, 1)$ and finds a representation without auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:wagp-st-form} states two more equivalent representations under R-WAPG intermediate form which are formulated as Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}.

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        For all $k\ge 0$, iterates $(w_k, y_k, x_{k + 1}, z_{k + 1})$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0$. Then 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_t)^{-1}\tau_t(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} 
            &= \theta_k(x_{k + 1} - x_k).
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{k + 1} &= 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            \\
            v_{k + 1} - x_{k + 1}
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            \\
            &= 
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            \\
            &= 
            (1 + \xi_k)^{-1}
            \left(
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right)
            \\
            &= 
            (1 + \xi_k)^{-1}\tau_k
            \left(
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right).
        \end{align*}
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
        \begin{align*}
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            \\
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            \\
            (1 + \xi_k) - L\delta_k
            &= 
            - \tau_k
            \\
            1 + \xi_k + \tau_k
            &=
            L\delta_k. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            = 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        \end{align*}
    \end{proof}

    \subsection{Narrowing it down}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
            Choose any $\gamma_1 \in (0, L]$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_i)_{i \in \N}, (x_i)_{i \in \N}, (v_i)_{i \in \N}$ and $(\rho_k)_{i \in \N}, (\alpha_k)_{i \in \N}$. 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 

@@

@@

                \rho_{k - 1}\alpha_{k - 1}^2

>>>>

        % We present a theoretical unification through the formulation of ``Relaxed weak accelerated proximal gradient algorithm (R-WAPG)'' which we invented. 
        % It unifies convergence claim for accelerated method for the strongly convex objective and Lipschitz smooth but non-strongly convex case, and it relaxes the conditions on the momentum sequence.

        % We connect the theories and practice by pointing out one practical exploits inspired the convergence proof of the algorithm which we called ``Spectral Momentum''. 
        % Numerical experiments are conducted to illustrate the theoretical convergence of R-WAPG and the performance of Spectral Momentum in with applications. 
        % We do net yet have a proof for the convergence of the algorithm in general.

@@

    \begin{definition}[Stepwise weak accelerated proximal gradient]\label{def:stepwise-wapg}\;\\
        Assume $0 \le \mu < L$.  
        Fix any $k \in \mathbb Z$. 
        For any $(v_k, x_k), \alpha_k \in (0, 1), \gamma > 0$, let $\hat \gamma$, and vectors $y_k, v_{k + 1}, x_{k + 1}$ be given by: 
        \begin{align*}
            \hat \gamma &= (1 - \alpha_k)\gamma + \mu \alpha_k, 
            \\
            y_k &= 
            (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= \hat\gamma^{-1}
            (\gamma(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}\label{obs:stepwise-wapg}
        Let's observe Definition \ref{def:stepwise-wapg} closely. 
        We make two crucial observations here. 
        We have $x_k, y_k, v_k$ lie on the same line because and they have the following equivalent equalities: 
        \begin{align*}
            (Q1): 
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k),
            \\
            (Q2): 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
    \end{observation}
        To see (Q1), observe 
        \begin{align*}
            y_k - v_k &= 
            \frac{\hat \gamma}{\alpha_k \gamma}(x_k - y_k)
            \\
            \iff 
            -(\alpha_k \gamma\hat \gamma^{-1} + 1)y_k
            &= 
            - \alpha_k \gamma \hat \gamma^{-1}v_k - x_k
            \\
            \iff 
            y_k &= 
            \frac{
                \alpha_k \gamma \hat \gamma^{-1}v_k + x_k
            }{1 + \alpha_k \gamma \hat \gamma^{-1}}
            \\
            &=  
            \frac{\alpha_k \gamma v_k + \hat \gamma x_k}{\gamma + \alpha_k \mu}.
        \end{align*}
        On the first equality (Q1), we multiplied both side of the equation by $\hat\gamma/\alpha_k \gamma$ and then group $y_k$ on the LHS. 
        The last equality comes by multiplying both the numerator and denominator by $\hat \gamma$, leaving the numerator $\hat \gamma + \alpha_k \gamma = \gamma + \alpha_k \mu$. 
        We used the definition of $\hat \gamma$ here. 
        To see the second equality (Q2), consider: 
        \begin{align*}
            y_k &= (\gamma + \alpha_k \mu)^{-1}(\alpha_k \gamma v_k + \hat\gamma x_k)
            \\
            \iff
            y_k - x_k &= 
            (\gamma + \alpha_k \mu)^{-1}
            (\alpha_k \gamma v_k - (\gamma + \alpha_k \mu)x_k + \hat \gamma x_k)
            \\
            \iff 
            (\gamma + \alpha_k \mu)(y_k - x_k)
            &= 
            \alpha_k\gamma v_k + 
            (\hat \gamma - \gamma - \alpha_k \mu) x_k
            \\
            &= \alpha_k \gamma v_k - \alpha_k \gamma x_k 
            \\
            &= \alpha_k \gamma(v_k - x_k)
            \\
            \iff 
            y_k - x_k &= 
            \frac{\alpha_k \gamma}{\gamma + \alpha_k \mu}(v_k - x_k). 
        \end{align*}
        On the second equality that follows the second $\iff$ we just substituted $\hat\gamma = (1 - \alpha_k)\gamma + \alpha_k \mu$. 
        Therefore, we discover that $x_k, v_k, y_k$ lies on the same line because (Q1) indicates $y_k - v_k$ parallels to $-(y_k - x_k)$ and both vector shares the same head which anchors at $y_k$.

@@

        Fix any integer $k \in \mathbb Z$, for any $v_k, x_k$, let $v_{k + 1}, x_{k + 1}, y_k, v_k, x_k, \hat \gamma$ be given by Definition \ref{def:stepwise-wapg}. 
        Choose any arbitrary $R_k \in \RR$.

@@

    \begin{definition}[Relaxed weak accelerated proximal gradient (R-WAPG)]\label{def:wapg}
        \;\\
        Initialize any $\gamma_1 \in (0, L]$, $(x_1, v_1)$. 
        Given auxiliary sequences $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ satisfying for all $k \ge 2$ the conditions: 
        \begin{align*}
            &\alpha_k \in (0, 1), 
            \\
            &\rho_k > 0, 
            \\
            &L\alpha_k^2 = (1 - \alpha_k)\rho_{k - 1}L \alpha_{k - 1}^2 + \mu \alpha_k , 
            \\
            &0 < \rho_k \alpha_k^2 < 1. 
        \end{align*}
        With base case $k = 1$ given by $\alpha_1 = (1 - \alpha_1)\gamma_1 + \mu \alpha_1$. 
        The algorithm generates a sequence of vector $(y_k, x_{k + 1}, v_{k + 1})_{k \ge 1}$ such that they satisfy for all $k\ge 1$: 
        \begin{align*}
            \gamma_k &:= \left.\begin{cases}
                \rho_{k -1}L\alpha_{k - 1}^2 & k \ge 2,
                \\
                \gamma_1 & k = 1. 
            \end{cases}\right\rbrace,
            \\
            \hat \gamma_{k + 1} &:= L\alpha_k^2, 
            \\
            y_k &= 
            (\gamma_k + \alpha_k \mu)^{-1}(\alpha_k \gamma_k v_k + \hat\gamma_{k + 1} x_k), 
            \\
            g_k &= \mathcal G_L y_k, 
            \\
            v_{k + 1} &= 
            \hat\gamma^{-1}_{k + 1}
            (\gamma_k(1 - \alpha_k) v_k - \alpha_k g_k + \mu \alpha_k y_k), 
            \\
            x_{k + 1} &= T_L y_k. 
        \end{align*}
    \end{definition}
    \begin{observation}
        Observe that if $\rho_k = 1$ for all $k\ge 0$, then the above algorithm is similar to (2.2.7) in Nesterov's book \cite{nesterov_lectures_2018}. 
        The initial condition is generic, so it can describe accelerated proximal gradient method in the middle of its executions. 
        \par
        Alternatively, any two of the vectors among $x_1, y_1, v_1$ can be used to initialize the algorithm because given $(v_1, y_1), (v_1, x_1)$, or $(x_1, y_1)$ we can solve 
        $y_1 = (\gamma_1 + \alpha_1\mu)^{-1}(\alpha_1 \gamma_1 v_1 + \hat \gamma_{2}x_1)$ for $x_1, y_1$ or $v_1$. 
        % \par
        % If one initial condition $x_0$ is given. 
        % Then $v_1 = x_0, x_1 = T_L x_0$ is considered a valid initial conditions. 
    \end{observation}

    \begin{observation}\label{obs:r-wapg-observation-1}
        If $\alpha_1 \in (0, 1)$ which is true by $\gamma_1 \in (0, L]$, then the entire sequence $\alpha_k \in (0, 1)$. 
        Suppose inductively that $\alpha_{k - 1}, \rho_{k - 1}$ are given such that they satisfy $\alpha_{k -1} \in (0, 1)$ and $0 < \rho_{k - 1} \alpha_{k - 1}^2 < 1$. 
        Solving the quadratic $L\alpha_k^2=(1 - \alpha_k)\rho_{k - 1}L\alpha_{k - 1}^2 + \mu \alpha_k$ for $\alpha_k$ yields candidates. 
        \begin{align*}
            \alpha_k &= 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                \pm
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right). 
        \end{align*}
        Choosing the positive sign which is the larger one of the roots of the quadratic. 
        We have $\alpha_k > 0$ because: 
        \begin{align*}
            \alpha_k &=
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right)
            \\
            &\ge 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \left|\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L\right|
            \right) + \alpha_{k - 1}\sqrt{\rho_{k - 1}}
            \\
            & > 0. 
        \end{align*}
        On the last strict inequality we used the fact that $\rho_{k - 1}> 0, \alpha_{k - 1} > 0$. 
        An upper bound can be identified by using inductive hypothesis and considering: 
        \begin{align*}
            \alpha_k &= 
            \frac{1}{2}\left(
                \frac{\mu}{L} - \rho_{k - 1}\alpha_{k - 1}^2 
                +
                \sqrt{(\rho_{k - 1}\alpha_{k - 1}^2 - \mu/L)^2 + 4\rho_{k - 1}\alpha_{k - 1}^2}
            \right)
            \\
            &<
            \frac{1}{2}\left(
                \frac{\mu}{L} + 
                \sup_{x \in (0, 1)}
                \left\lbrace
                    -x + \sqrt{(x - \mu/L)^2 + 4x}
                \right\rbrace
            \right)
            \\
            & \le \frac{1}{2}\left(
                \mu/L + \max\left(\mu/L, -1 + \sqrt{(1 - \mu/L)^2 + 4}\right)
            \right) \le 1. 
        \end{align*}
        Going to the first inequality, we used $\rho_{k - 1} \alpha_{k - 1}^2 < 1$ to get the strict inequality. 
        Going from the second to the third inequality, we maximized $\mu/L$ by monotone increasing of linear function and the square root function. 
        Therefore, inductively, $\alpha_k \in (0, 1)$ holds. 
        However, the limit of $\alpha_k$ could be 1. 
    \end{observation}

    \begin{proposition}[R-WAPG convergence claim]\label{prop:wagp-convergence}\; \\
        Given any $(v_1, x_1)$, let vectors $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ and scalars sequence $(\alpha_k)_{k \ge 1}, (\rho_k)_{k \ge 1}$ be generated by R-WAPG (Definition \ref{def:wapg}). 

@@

        Recall the stepwise convergence theorem, since the choice of $\gamma, \hat \gamma$ is satisfies is strictly positive and for $i=2, 3, \cdots, k$, by Definition \ref{def:wapg} it has $\gamma = \rho_{i - 1} L \alpha_{i - 1}^2 > 0, \hat \gamma = L \alpha_i^2 > 0$ at each step, with the base case $i = 1$: $\gamma \in (0, L], \hat \gamma = (1 - \alpha_1)\gamma + \mu \alpha_1$. 
        Since $\alpha_i \in(0, 1)$ for all $i = 1, \cdots, k$, because of Observation \ref{obs:r-wapg-observation-1}, we can use Proposition \ref{prop:stepwise-lyapunov}, to show that for all $k \ge 1$: 

@@

        Additionally, for all $k \ge 1$ the algorithm converges by considering $R_{k + 1}$: 

@@

\section{Equivalent representations of R-WAPG}
    This section reduces Definition \ref{def:wapg} into simpler forms that are comparable to what commonly appears in the literatures. 
    Proposition \ref{prop:wapg-first-equivalent-repr} simplifies Definition \ref{def:wapg} for the specific initial conditions $\gamma_0 \in(0, 1)$ and finds a representation without auxiliary sequence $\gamma_k, \hat \gamma_k$. 
    Definition \ref{def:r-wapg-intermediate} states the first simplified form of the R-WAPG algorithm which we call: ``R-WAPG intermediate form''. 
    Following a similar pattern, Proposition \ref{prop:wagp-st-form}, \ref{prop:wagp-st-form} states two more equivalent representations under R-WAPG intermediate form which are formulated as Definition \ref{def:r-wapg-st-form}, \ref{def:r-wapg-momentum-form}. 
    Proposition \ref{prop:wagp-convergence} applies to all these equivalent forms.

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$. 
        for all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0\; \forall k \ge 1$. 
        Then for all $k \ge 1$: 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} 
            &= \theta_k(x_{k + 1} - x_k).
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{k + 1} &= 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            \\
            v_{k + 1} - x_{k + 1}
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            \\
            &= 
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            \\
            &= 
            (1 + \xi_k)^{-1}
            \left(
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right)
            \\
            &= 
            (1 + \xi_k)^{-1}\tau_k
            \left(
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right).
        \end{align*}
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
        \begin{align*}
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            \\
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            \\
            (1 + \xi_k) - L\delta_k
            &= 
            - \tau_k
            \\
            1 + \xi_k + \tau_k
            &=
            L\delta_k. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            = 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        \end{align*}
    \end{proof}

    \subsection{Narrowing it down}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
            Assume $\mu < L$. 
            Choose any $\gamma_1 \in (0, L], x_1, v_1$ as the initial condition for R-WAPG (Definition \ref{def:wapg}) to produce vectors sequence $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$. 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge1}$, and for all $k\ge 1$ they are algebraically equivalent to
            \begin{align*}
                & 
                y_{k} = 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                & x_{k + 1} = 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                & v_{k + 1} = 
                \left(
                    1 + \frac{\mu}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
            \end{align*}

@@

            For all $k \ge 1$, by R-WAPG (Definition \ref{def:wapg}), it has: 

@@

                \gamma_k/L
